Characterisation of MSC in clinical trial reports: analysis of published descriptors

### 2020-06-28 paper2_figures.Rmd
updates to figures; removal of JIF and HDI data

### each panel figure 2
```{r fig2}
#by country
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(country, n), y = n)) +
  geom_bar(stat = "identity", fill = pal[4],
           size = 0, width = 0.8) +
  xlab("") +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 15, 5),
                     minor_breaks = seq(0, 15, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by phase
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(phase,n), y = n)) +
  geom_bar(stat = "identity", fill = pal[4], size = 0, width = 0.8) +
  xlab("") +
 # geom_text(aes(y = n + 4, label = pc) ) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 35, 10),
                     minor_breaks = seq(0, 35, 1),
                     limits = c(0, 35),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by indication
indication_bar <- summary_indication %>% 
  ggplot(aes(x = reorder(indication, n), y = n)) +
  geom_bar(stat = "identity", fill = pal[4], size = 0, width = 0.8) +
  xlab("") +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 12, 2),
                     minor_breaks = seq(0, 12, 2),
                     limits = c(0, 13),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by route
route_bar <- summary_route %>% 
  ggplot(aes(x = reorder(route, n), y = n)) +
  geom_bar(stat = "identity", fill = pal[4], size = 0, width = 0.8) +
  xlab("") +
#  geom_text(aes(y = n + 3, label = pc) ) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 25, 5),
                     minor_breaks = seq(0, 25, 1),
                     limits = c(0, 25),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

@@

layout <- "
a#
a#
ad
ad
ad
ad
ad
bd
bd
bd
bd
cd
cd
cd
"

fig2 <- country_bar  + route_bar+ phase_bar+ indication_bar +
  plot_layout(design = layout) +
  plot_annotation(caption = "Number of Articles",
                  tag_levels = "A")&
    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
          plot.caption = element_text(size = 9, hjust = 0.5, face = "plain"))

ggsave("figs/fig_2.svg", 
       plot = fig2, 
       device = device,
       width = fig_w_2, 
       height = fig_h*2,
       units = units)

@@

```{r fig_3}
# source
source_bar <- summary_source %>% 
  ggplot(aes(x = source, y = n)) +
  geom_bar(stat = "identity",fill = pal[4], size = 0, width = 0.8) +
  scale_y_continuous(name = "Number of Articles",
                    breaks = seq(0, 50, 10),
                    minor_breaks = seq(0, 50, 10),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black",
                                  angle = 285, vjust = 0.5, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())

# allo - auto
allo_auto_bar <- summary_allo_auto %>% 
  ggplot(aes(x = allo_auto, y = n)) +
  geom_bar(stat = "identity",fill = pal[4], size = 0, width = 0.8) +
  scale_y_continuous(name = NULL,
                    breaks = seq(0, 50, 10),
                    minor_breaks = seq(0, 50, 10),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black", 
                                  angle = 285, vjust = 0.5, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())

# stem_stomal
stem_stromal_bar <- summary_stem_stromal %>%
  ggplot(aes(x = stem_stromal, y = n)) +
  geom_bar(stat = "identity",fill = pal[4], size = 0, width = 0.8) +
  scale_y_continuous(name = NULL,
                    breaks = seq(0, 50, 10),
                    minor_breaks = seq(0, 50, 10),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black", 
                                   angle = 285, vjust = 0.5, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())
```

@@

ggsave("figs/fig_3.svg", 
       plot = fig3, 
       device = device,
       width = fig_w_1.5, 
       height = fig_h,
       units = units)
```

@@

# change levels of status and markers.
# markers
# process test_col names
test_cols <- str_replace(test_cols, "_test", "")
# set the levels in that order
test_by_attribute$marker2 <- factor(test_by_attribute$marker2, 
                                    levels = test_cols)
test_by_attribute$ref_number <- factor(test_by_attribute$ref_number, 
                                    levels = c(levels(test_by_attribute$ref_number), "Total P", "Total M"))
# status
# recode status
test_by_attribute <- test_by_attribute %>%
  mutate(test_status = recode_factor(status,
                                     p = "Performed, value reported (by batch or average)",
                                     m = "Performed, no value reported",
                                     n = "Not performed"))

@@

# panel c
diffmoasum <- dat %>% group_by(MOA, differentiation) %>% 
  summarise(n = length(differentiation))
```

@@

```{r}
# panel a
fig6a <- functionality %>% 
  ggplot() +
  geom_bar(aes(x = type, y = n, fill = status, label = pc),
           stat = "identity") +
  scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)]),
                    name = " Functionality assessment",
                    guide = guide_legend(nrow = 3, title.position = "top", title.hjust = 0.5 )) +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 80, 10),
                     minor_breaks = seq(0, 80, 10),
                     limits = c(0, 85),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0.5), name = NULL) +
  geom_text(data = filter(functionality, status == "Not mentioned"), aes(x = type, 50, label = pc) ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()

# panel b
fig6b <- moa_isct_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal, 
                    guide = guide_legend(nrow = 4, title = NULL)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 40, 5),
                     minor_breaks = seq(0, 40, 5),
                     limits = c(0, 40),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Mechanism of action") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()

# panel c
fig6c <- diffmoasum %>%
  ggplot(aes(x = MOA, y = n, fill = differentiation)) +
  geom_bar(stat = "identity", size = 0) +
   scale_fill_manual(values = c("#BABABA", pal[5]), 
                    name = "Differentiation capacity",
                    labels = c("Not demonstrated", "Demonstrated"),
                    guide = guide_legend(nrow = 2, 
                                         title.position = "top",
                                         title.hjust = 0.5)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 40, 5),
                     minor_breaks = seq(0, 40, 5),
                     limits = c(0, 40),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL, labels =NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()

>>>>

### each panel figure 2
```{r fig2}
#by country
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(country, n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4],
           fill = "black",
           size = 0, width = 0.8) +
  xlab("") +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 15, 5),
                     minor_breaks = seq(0, 15, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by phase
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(phase,n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4],
           fill = "black",
           size = 0, 
           width = 0.8) +
  xlab("") +
 # geom_text(aes(y = n + 4, label = pc) ) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 35, 10),
                     minor_breaks = seq(0, 35, 1),
                     limits = c(0, 35),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by indication
indication_bar <- summary_indication %>% 
  ggplot(aes(x = reorder(indication, n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4], 
           fill = "black", 
           size = 0, 
           width = 0.8) +
  xlab("") +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 12, 2),
                     minor_breaks = seq(0, 12, 2),
                     limits = c(0, 13),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

# by route
route_bar <- summary_route %>% 
  ggplot(aes(x = reorder(route, n), y = n)) +
  geom_bar(stat = "identity", 
           # fill = pal[4],
            fill = "black",
           size = 0, 
           width = 0.8) +
  xlab("") +
#  geom_text(aes(y = n + 3, label = pc) ) +
  scale_y_continuous(name = NULL, 
                     breaks = seq(0, 25, 5),
                     minor_breaks = seq(0, 25, 1),
                     limits = c(0, 25),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

@@

layout <- "
a#
a#
ad
ad
ad
ad
ad
bd
bd
bd
cd
cd
cd
cd
"

fig2 <- country_bar + phase_bar + route_bar + indication_bar +
  plot_layout(design = layout) +
  plot_annotation(caption = "Number of Articles",
                  tag_levels = "A")&
    theme(plot.tag = element_text(size = 9, hjust = 0, face = "bold"),
          plot.caption = element_text(size = 9, hjust = 0.5, face = "plain"))

ggsave("figs/fig_2_black.svg", 
       plot = fig2, 
       device = device,
       width = fig_w_2, 
       height = fig_h*2,
       units = units)

@@

```{r fig_3}
# source
source_bar <- summary_source %>% 
  ggplot(aes(x = source, y = n)) +
  geom_bar(stat = "identity",
           # fill = pal[4],
           fill = "black",
           size = 0, 
           width = 0.8) +
  scale_y_continuous(name = "Number of Articles",
                    breaks = seq(0, 50, 10),
                    minor_breaks = seq(0, 50, 10),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black",
                                  angle = 285, vjust = 0.5, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())

# allo - auto
allo_auto_bar <- summary_allo_auto %>% 
  ggplot(aes(x = allo_auto, y = n)) +
  geom_bar(stat = "identity",
           # fill = pal[4], 
           fill = "black",
           size = 0, 
           width = 0.8) +
  scale_y_continuous(name = NULL,
                    breaks = seq(0, 50, 10),
                    minor_breaks = seq(0, 50, 10),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black", 
                                  angle = 285, vjust = 0.5, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())

# stem_stomal
stem_stromal_bar <- summary_stem_stromal %>%
  ggplot(aes(x = stem_stromal, y = n)) +
  geom_bar(stat = "identity",
           # fill = pal[4], 
           fill = "black",
           size = 0, 
           width = 0.8) +
  scale_y_continuous(name = NULL,
                    breaks = seq(0, 50, 10),
                    minor_breaks = seq(0, 50, 10),
                    limits = c(0, 60),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black", 
                                   angle = 285, vjust = 0.5, hjust = 0),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank())
```

@@

ggsave("figs/fig_3_black.svg", 
       plot = fig3, 
       device = device,
       width = fig_w_1.5, 
       height = fig_h,
       units = units)
```

@@

# change levels of status and markers.
# markers
# process test_col names
test_cols <- str_replace(test_cols, "_test", "")
# set the levels in that order
test_by_attribute$marker2 <- factor(test_by_attribute$marker2, 
                                    levels = test_cols)
test_by_attribute$ref_number <- factor(test_by_attribute$ref_number)
# status
# recode status
test_by_attribute <- test_by_attribute %>%
  mutate(test_status = recode_factor(status,
                                     p = "Performed, value reported (by batch or average)",
                                     m = "Performed, no value reported",
                                     n = "Not performed"))

@@

moa_isct_summary$stem_stromal <- fct_relevel(moa_isct_summary$stem_stromal,
                                         "Stem",
                                         "Stromal",
                                         "Multipotent Stromal",
                                         "Regenerative")

moa_isct_summary$MOA <- fct_relevel(moa_isct_summary$MOA,
                                    "Not stated",
                                    "Multiple",
                                    "Differentiation",
                                    "Immune",
                                    "Paracrine")

# panel c
diffmoasum <- dat %>% group_by(MOA, differentiation) %>% 
  summarise(n = length(differentiation))

diffmoasum$MOA <- fct_relevel(diffmoasum$MOA,
                                     "Not stated",
                                    "Multiple",
                                    "Differentiation",
                                    "Immune",
                                    "Paracrine")

diffmoasum$differentiation <- fct_relevel(diffmoasum$differentiation,
                                          "No",
                                          "Yes")

@@

```{r}
# panel a
fig6a <- functionality %>% 
  ggplot() +
  geom_bar(aes(x = type, y = n, fill = status, label = pc),
           stat = "identity", size = 0) +
  scale_fill_manual(values =  c("#BABABA", pal[c(3, 5)]),
                    name = " Functionality",
                    guide = guide_legend(nrow = 4,
                                         title.position = "top",
                                         title.hjust = 0 )) +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 80, 10),
                     minor_breaks = seq(0, 80, 10),
                     limits = c(0, 85),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0.5), name = NULL) +
  geom_text(data = filter(functionality, 
                          status == "Not mentioned"),
            aes(x = type, 50, label = pc) ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 30),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()

# panel b
fig6b <- moa_isct_summary %>% 
  ggplot(aes(x = MOA, y = n, fill = stem_stromal)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal, 
                    name = "Nomenclature",
                    guide = guide_legend(nrow = 4,
                                         title.position = "top",
                                         title.hjust = 0 )) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 40, 5),
                     minor_breaks = seq(0, 40, 5),
                     limits = c(0, 42),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "MOA") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 0, l = 0),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()

# panel c
fig6c <- diffmoasum %>%
  ggplot(aes(x = MOA, y = n, fill = differentiation)) +
  geom_bar(stat = "identity", size = 0) +
   scale_fill_manual(values = c("#BABABA", pal[5]), 
                    name = "Differentiation capacity",
                    labels = c("Not demonstrated", "Demonstrated"),
                    guide = guide_legend(nrow = 4, 
                                         title.position = "top",
                                         title.hjust = 0)) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 40, 5),
                     minor_breaks = seq(0, 40, 5),
                     limits = c(0, 42),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = NULL, labels =NULL) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        plot.margin = margin(t = 0, r = 0, l = 0),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 8, colour = "black"),
        legend.key.size = unit(0.1, "in")) +
  coord_flip()
